Fusion Moves for Correlation Clustering

### 2014-11-11 paper/inputs/fig_fusion.tex
changed fig style

            \draw (2-2,2+4) node[nS] (n0) {$0$}; 
            \draw (4-2,2+4) node[nS] (n1) {$1$};
            \draw (2-2,0+4) node[nS] (n3) {$2$}; 
            \draw (4-2,0+4) node[nS] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eCC] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eCC] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2-2,2) node[nS] (n0) {$0$}; 
            \draw (4-2,2) node[nS] (n1) {$1$};
            \draw (2-2,0) node[nS] (n3) {$2$}; 
            \draw (4-2,0) node[nS] (n4) {$3$};
            \path
                (n0) edge[eCC] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eCC] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            % first segmentation as coloring
            \draw (2+4,2+4) node[nS,fill=red!60] (n0) {$0$}; 
            \draw (4+4,2+4) node[nS,fill=red!60] (n1) {$1$};
            \draw (2+4,0+4) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4+4,0+4) node[nS,fill=green!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            % 1. FUSION
            \draw (2+4,2) node[nS,fill=red!60] (n0) {$0$}; 
            \draw (4+4,2) node[nS,fill=green!60] (n1) {$1$};
            \draw (2+4,0) node[nS,fill=red!60] (n3) {$2$}; 
            \draw (4+4,0) node[nS,fill=green!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+4,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
            \draw (4+4,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
            \draw (2+4,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
            \draw (4+4,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            % 2. FUSION
            \draw (2+8,2) node[nS,fill=red!60] (n0) {$0$}; 
            \draw (4+8,2) node[nS,fill=blue!60] (n1) {$1$};
            \draw (2+8,0) node[nS,fill=red!60] (n3) {$2$}; 
            \draw (4+8,0) node[nS,fill=blue!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+8,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
            \draw (4+8,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
            \draw (2+8,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
            \draw (4+8,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            % 3. FUSION
            \draw (2+12,2) node[nS,fill=green!60] (n0) {$0$}; 
            \draw (4+12,2) node[nS,fill=red!60] (n1) {$1$};
            \draw (2+12,0) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4+12,0) node[nS,fill=red!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+12,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
            \draw (4+12,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
            \draw (2+12,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
            \draw (4+12,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            % 4. FUSION
            \draw (2+16,2) node[nS,fill=green!60] (n0) {$0$}; 
            \draw (4+16,2) node[nS,fill=blue!60] (n1) {$1$};
            \draw (2+16,0) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4+16,0) node[nS,fill=blue!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+16,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
            \draw (4+16,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
            \draw (2+16,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
            \draw (4+16,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            % 5. FUSION
            \draw (2+20,2) node[nS,fill=blue!60] (n0) {$0$}; 
            \draw (4+20,2) node[nS,fill=red!60] (n1) {$1$};
            \draw (2+20,0) node[nS,fill=blue!60] (n3) {$2$}; 
            \draw (4+20,0) node[nS,fill=red!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+20,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
            \draw (4+20,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
            \draw (2+20,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
            \draw (4+20,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            % 6. FUSION
            \draw (2+24,2) node[nS,fill=blue!60] (n0) {$0$}; 
            \draw (4+24,2) node[nS,fill=green!60] (n1) {$1$};
            \draw (2+24,0) node[nS,fill=blue!60] (n3) {$2$}; 
            \draw (4+24,0) node[nS,fill=green!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+24,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
            \draw (4+24,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
            \draw (2+24,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
            \draw (4+24,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            % 7. FUSION
            \draw (2+28,2) node[nS,fill=blue!60] (n0) {$0$}; 
            \draw (4+28,2) node[nS,fill=yellow!60] (n1) {$1$};
            \draw (2+28,0) node[nS,fill=blue!60] (n3) {$2$}; 
            \draw (4+28,0) node[nS,fill=yellow!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+28,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
            \draw (4+28,2-4) node[nD, circle split part fill={red!60, yellow!60}] (n1) {$ $};
            \draw (2+28,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
            \draw (4+28,0-4) node[nD, circle split part fill={green!60, yellow!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

>>>>

            \draw (2-2,2+4) node[nS] (n0) {$0$}; 
            \draw (4-2,2+4) node[nS] (n1) {$1$};
            \draw (2-2,0+4) node[nS] (n3) {$2$}; 
            \draw (4-2,0+4) node[nS] (n4) {$3$};
            \path
                (n0) edge[eNotCut] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eNotCut] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eCut] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eCut] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2-2,2) node[nS] (n0) {$0$}; 
            \draw (4-2,2) node[nS] (n1) {$1$};
            \draw (2-2,0) node[nS] (n3) {$2$}; 
            \draw (4-2,0) node[nS] (n4) {$3$};
            \path
                (n0) edge[eCut] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eCut] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eNotCut] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eNotCut] node[eNS]{$w_{13}$} (n4)
            ;

            % first segmentation as coloring
            \draw (2+4,2+4) node[nS,fill=red!60] (n0) {$0$}; 
            \draw (4+4,2+4) node[nS,fill=red!60] (n1) {$1$};
            \draw (2+4,0+4) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4+4,0+4) node[nS,fill=green!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 1. FUSION
            \draw (2+4,2) node[nS,fill=red!60] (n0) {$0$}; 
            \draw (4+4,2) node[nS,fill=green!60] (n1) {$1$};
            \draw (2+4,0) node[nS,fill=red!60] (n3) {$2$}; 
            \draw (4+4,0) node[nS,fill=green!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+4,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
            \draw (4+4,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
            \draw (2+4,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
            \draw (4+4,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 2. FUSION
            \draw (2+8,2) node[nS,fill=red!60] (n0) {$0$}; 
            \draw (4+8,2) node[nS,fill=blue!60] (n1) {$1$};
            \draw (2+8,0) node[nS,fill=red!60] (n3) {$2$}; 
            \draw (4+8,0) node[nS,fill=blue!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+8,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
            \draw (4+8,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
            \draw (2+8,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
            \draw (4+8,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 3. FUSION
            \draw (2+12,2) node[nS,fill=green!60] (n0) {$0$}; 
            \draw (4+12,2) node[nS,fill=red!60] (n1) {$1$};
            \draw (2+12,0) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4+12,0) node[nS,fill=red!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+12,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
            \draw (4+12,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
            \draw (2+12,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
            \draw (4+12,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 4. FUSION
            \draw (2+16,2) node[nS,fill=green!60] (n0) {$0$}; 
            \draw (4+16,2) node[nS,fill=blue!60] (n1) {$1$};
            \draw (2+16,0) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4+16,0) node[nS,fill=blue!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+16,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
            \draw (4+16,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
            \draw (2+16,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
            \draw (4+16,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 5. FUSION
            \draw (2+20,2) node[nS,fill=blue!60] (n0) {$0$}; 
            \draw (4+20,2) node[nS,fill=red!60] (n1) {$1$};
            \draw (2+20,0) node[nS,fill=blue!60] (n3) {$2$}; 
            \draw (4+20,0) node[nS,fill=red!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+20,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
            \draw (4+20,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
            \draw (2+20,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
            \draw (4+20,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 6. FUSION
            \draw (2+24,2) node[nS,fill=blue!60] (n0) {$0$}; 
            \draw (4+24,2) node[nS,fill=green!60] (n1) {$1$};
            \draw (2+24,0) node[nS,fill=blue!60] (n3) {$2$}; 
            \draw (4+24,0) node[nS,fill=green!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+24,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
            \draw (4+24,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
            \draw (2+24,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
            \draw (4+24,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 7. FUSION
            \draw (2+28,2) node[nS,fill=blue!60] (n0) {$0$}; 
            \draw (4+28,2) node[nS,fill=yellow!60] (n1) {$1$};
            \draw (2+28,0) node[nS,fill=blue!60] (n3) {$2$}; 
            \draw (4+28,0) node[nS,fill=yellow!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+28,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
            \draw (4+28,2-4) node[nD, circle split part fill={red!60, yellow!60}] (n1) {$ $};
            \draw (2+28,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
            \draw (4+28,0-4) node[nD, circle split part fill={green!60, yellow!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

### 2014-11-11 paper/inputs/fig_hc_alg.tex
changed fig style

\tikzstyle{nS}=[circle,minimum size = 0.6cm,inner sep = 0pt,draw, font=\small,align=left]
\tikzstyle{eS}=[thick,minimum size = 0.5cm,inner sep = 0pt,draw, font=\small,align=left]
\tikzstyle{eC}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=red, font=\small,align=left]
\tikzstyle{eNC}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=green, font=\small,align=left]
\tikzstyle{eNS}=[fill=white,minimum size = 0.5cm,inner sep = 0pt, font=\tiny,align=left]

@@

    \path
        (n0) edge[eS] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eS] node[eNS]{$w_{12}=-2$} (n2) 
        (n3) edge[eS] node[eNS]{$w_{34}=-2$} (n4) 
        (n4) edge[eS] node[eNS]{$w_{45}=1$} (n5)
        (n0) edge[eC] node[eNS]{$w_{03}=4$} (n3)
        (n1) edge[eS] node[eNS]{$w_{14}=2$} (n4)
        (n2) edge[eS] node[eNS]{$w_{25}=3$} (n5)
    ;
    \end{tikzpicture}
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,2) node[nS] (n2) {$2$};
    \draw (4,0) node[nS] (n4) {$4$};
    \draw (6,0) node[nS] (n5) {$5$};

    \path
        (n03) edge[eS] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eS] node[eNS]{$w_{12}=-2$} (n2) 
        (n03) edge[eS] node[eNS]{$w_{34}-2$} (n4) 
        (n4) edge[eS] node[eNS]{$w_{45}=1$} (n5)
        (n1) edge[eS] node[eNS]{$w_{14}=2$} (n4)
        (n2) edge[eC] node[eNS]{$w_{25}=3$} (n5)
    ;
    \end{tikzpicture}
}
%
\resizebox{!}{0.15\linewidth}{%
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,1) node[nS] (n25) {$\{2,5\}$};
    \draw (4,0) node[nS] (n4) {$4$};
    \path
        (n03) edge[eS] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eS] node[eNS]{$w_{12}=-2$} (n25) 
        (n03) edge[eS] node[eNS]{$w_{34}=-2$} (n4) 
        (n4) edge[eS] node[eNS]{$w_{45}=1$} (n25)
        (n1) edge[eC] node[eNS]{$w_{14}=2$} (n4)
    ;
    \end{tikzpicture}
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,1) node[nS] (n14) {$\{1,4\}$};
    \draw (6,1) node[nS] (n25) {$\{2,5\}$};
    \path
        %(n03) edge[eS] node[eNS]{$w_{01}$} (n1) 
        (n14) edge[eNC] node[eNS]{$w_{12}+$\\$w_{45}=$\\$-1$} (n25) 
        (n03) edge[eS] node[eNS]{$w_{01}+$\\$w_{34}=$\\$-3$} (n14) 
    ;
    \end{tikzpicture}
}
\caption{
    To use hierarchical clustering as an approximator for
    the multicut objective we contract the edge with the highest weight
    in each step (to be contracted edge is shown in red). 
    Whenever multiple edges are merged into a single edge,
    we use the sum of the weight as a new weight, since
    we have to pay for all edges which are cut in the uncontracted 
    graph.
    We stop when the highest edge weight is smaller
    or equal to zero (edge shown in green).
}\label{fig:hc_alg}
\end{figure*}
\end{center}

>>>>

\tikzstyle{nS}=[circle,minimum size = 0.6cm,inner sep = 0pt,draw, font=\small,align=left]

@@

    \path
        (n0) edge[eCut] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eCut] node[eNS]{$w_{12}=-2$} (n2) 
        (n3) edge[eCut] node[eNS]{$w_{34}=-2$} (n4) 
        (n4) edge[eCut] node[eNS]{$w_{45}=1$} (n5)
        (n0) edge[eNotCut] node[eNS]{$w_{03}=4$} (n3)
        (n1) edge[eCut] node[eNS]{$w_{14}=2$} (n4)
        (n2) edge[eCut] node[eNS]{$w_{25}=3$} (n5)
    ;
    \end{tikzpicture}
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,2) node[nS] (n2) {$2$};
    \draw (4,0) node[nS] (n4) {$4$};
    \draw (6,0) node[nS] (n5) {$5$};

    \path
        (n03) edge[eCut] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eCut] node[eNS]{$w_{12}=-2$} (n2) 
        (n03) edge[eCut] node[eNS]{$w_{34}-2$} (n4) 
        (n4) edge[eCut] node[eNS]{$w_{45}=1$} (n5)
        (n1) edge[eCut] node[eNS]{$w_{14}=2$} (n4)
        (n2) edge[eNotCut] node[eNS]{$w_{25}=3$} (n5)
    ;
    \end{tikzpicture}
}
%
\resizebox{!}{0.15\linewidth}{%
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,1) node[nS] (n25) {$\{2,5\}$};
    \draw (4,0) node[nS] (n4) {$4$};
    \path
        (n03) edge[eCut] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eCut] node[eNS]{$w_{12}=-2$} (n25) 
        (n03) edge[eCut] node[eNS]{$w_{34}=-2$} (n4) 
        (n4) edge[eCut] node[eNS]{$w_{45}=1$} (n25)
        (n1) edge[eNotCut] node[eNS]{$w_{14}=2$} (n4)
    ;
    \end{tikzpicture}
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,1) node[nS] (n14) {$\{1,4\}$};
    \draw (6,1) node[nS] (n25) {$\{2,5\}$};
    \path
        %(n03) edge[eCut] node[eNS]{$w_{01}$} (n1) 
        (n14) edge[eBlue] node[eNS]{$w_{12}+$\\$w_{45}=$\\$-1$} (n25) 
        (n03) edge[eCut] node[eNS]{$w_{01}+$\\$w_{34}=$\\$-3$} (n14) 
    ;
    \end{tikzpicture}
}
\caption{
     To use hierarchical clustering as an approximator for
    the multicut objective we contract the edge with the highest weight
    in each step (to be contracted edge is shown in green).
    Whenever multiple edges are merged into a single edge,
    we use the sum of the weight as a new weight, since
    we have to pay for all edges which are cut in the uncontracted
    graph.
    We stop when the highest edge weight is smaller
    or equal to zero (edge shown in blue).
}\label{fig:hc_alg}
\end{figure*}
\end{center}
